A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-03-19 graph_syntax.tex
more updates to the designvars,constraints,objectives section

More formally, all inputs that have no incomming fixed or explicit edges are defined
as design variables.

Objective and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
athrimetic opperations to form the final objective function. For example, the problem from 
Fig. [insert ref] might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer explictly identifies variables 
or groups of variables and assigns an simple, explicit relationship between them.

For the proposed syntax objectives and constraints are represented through the use of 
expression nodes. These nodes contain the actual mathematical expression used to define the 
objective or constraint value. You can distinguish between an objective or constraint node 
via the presence of a simple expression (objective) vs an inequality/equality (constraint). 
Fig. [insert new ref] shows the notional problem graph augmented with objective and 
constraint values.

>>>>

More formally, all inputs that have no incomming fixed or explicit edges are defined
as design variables. When working with a MCG or FPF, only fixed and explicit edges are allowed, 
in which case a design variable is simply a variable node with no incomming edges. For a SPF 
any design variable node would have at least one incomming implicit edge from a driver node.

Objective and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
athrimetic opperations to form the final objective function. For example, the problem from 
Fig. \ref{f:design vars} might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer explictly identifies variables 
or groups of variables and assigns an simple, explicit relationship between them.

For the proposed syntax objectives and constraints are represented through the use of 
expression nodes. These nodes contain the actual mathematical expression used to define the 
objective or constraint value. Objective or constraint nodes are distinguished
via the presence of a simple expression (objective) vs an inequality/equality (constraint). 
Fig. [insert ref] shows the notional problem graph augmented with objective and 
constraint values.
